\cvsection{Work Experience}
\begin{cventries}
  \cventry
    {Computer Science Departament}
    {Teaching Assistant}
    {Valparaíso, Chile}
    {Jul. 2016 - Present}
    {
      \begin{cvitems}
        \item {Proposed and teaching a new course called Software Deployment on Linux. Some of the tools used were: Docker, Kubernetes, AWS, Django, PHP, and Nginx. As a result, the students acquire practical and useful skills to deploy their applications.}
        \item {Teaching the course Operating System. In this course, the students learn the main concepts of the operating systems by practice using a Linux environment and related tools DevOps.}
      \end{cvitems}
    }
    
    
  \cventry
    {Chilean Virtual Observatory (ChiVO)}
    {DevOps}
    {Valparaíso, Chile}
    {Jan. 2018 - May. 2018}
    {
      \begin{cvitems}
        \item {The FONDEF IT15I10041 project seeks to achieve the implementation of a virtual observatory in Chile that complies with the standards and protocols defined by the International Virtual Observatory Alliance (IVOA).}
        \item {We proposed and implemented a Cloud service where astronomers can safely use Jupyter notebooks over a personal space designed for high-performance processing using Docker Containers and Kubernetes.}
      \end{cvitems}
    }
    

  \cventry
    {Linets}
    {Systems Engineer}    
    {Santiago, Chile}
    {Jan. 2014 - Mar. 2016}
    {
      \begin{cvitems}
        \item {System Administrator for upkeep, configuration, and reliable operation of 400 servers. The usual tasks were: troubleshooting, configuration, database administration, and optimization for the servers.}
        \item {Worked with OpenStack and main components to build the first OpenStack deployment in Chile which backs Beebop, the first public cloud in Chile.}
        \item {Automatic Deployment of OpenStack using Docker Containers and Ansible playbooks.}
        \item {Implementation of a shared storage for the public cloud using Ceph. Ceph is a unified, distributed storage system designed for excellent performance, reliability, and scalability.}
      \end{cvitems}
    }
    
  \cventry
    {Computer Science Departament}
    {Systems Administrator}    
    {Valparaíso, Chile}
    {Aug. 2011 - Oct. 2014}
    {
      \begin{cvitems}
		\item{System Administrator for the internal servers, maintaining all the services to ensure its availability to students and teachers.}
      \end{cvitems}
    }    
\end{cventries}
