\cvsection{Work Experience}
\begin{cventries}

  \cventry
    {The University of Texas at Austin}
    {Software Developer Consultant}
    {Austin, TX}
    {Mar 2021 - Present}
    {
      \begin{cvitems}
        \item{Planet Texas 2050 is an eight-year sprint to find solutions that will make our communities more resilient and better prepared. To do that, we’re bringing together architects, archaeologists, city planners, public health experts, geologists, engineers, computer scientists, artists — and more.}
        \item{Refactor metadata APIs which improve the performance of the APIs and make them more maintainable using LoopBack 4, TypeScript, OpenAPI, and PostgreSQL}
        \item{Design and build a web application which allows users to run simulations on High Performance Computing (HPC) clusters without using a SSH. The application is built using FastAPI and React}
      \end{cvitems}
    }

  \cventry
    {Information Sciences Institute}
    {Software Developer Consultant}
    {Los Angeles, USA}
    {Apr 2021 - Present / Jan. 2019 - May 2019}
    {
      \begin{cvitems}
        \item{Collabrate and develop in the Model INTegration project (MINT), MINT project combine existing models from various disciplines-including hydrology, agriculture, economics and social sciences-and run simulations to predict the consequences of actions or policies in specific geographic regions.}
        \item {Develop services (APIs, pipelines, workflows) to integrate data from different sources using Python, FastAPI, Express, and PostgreSQL}
        \item {Develop Helm charts to deploy services in Kubernetes clusters}
        \item {Maintain and improve the CI/CD pipelines using GitHub Actions}
        \item {Deploy and maintain authentication services using Keycloak}
        \item {Integrate new execution system to run simulations in HPC clusters using APIs}
      \end{cvitems}
    }

  \cventry
    {Information Sciences Institute}
    {Research Programmer}
    {Los Angeles, USA}
    {Jul. 2019 - Oct. 2020}
    {
      \begin{cvitems}
        \item{Collabrate and develop in the Model INTegration project (MINT), MINT project combine existing models from various disciplines-including hydrology, agriculture, economics and social sciences-and run simulations to predict the consequences of actions or policies in specific geographic regions.}
      \end{cvitems}
    }

  \cventry
    {Computer Science Department}
    {Part-time Teacher}
    {Valparaíso, Chile}
    {Jul. 2016 - Present}
    {
      \begin{cvitems}
        \item {Proposed and teaching a new course called Software Deployment on Linux. Some of the tools used were: Docker, Kubernetes, AWS, GitHub Actions, Django, PHP, and Nginx. As a result, the students acquire practical and useful skills to deploy their applications.}
        \item {Teaching the course Operating System. In this course, the students learn the main concepts of the operating systems by practice using a Linux environment and related tools DevOps.}
      \end{cvitems}
    }


  \cventry
    {Chilean Virtual Observatory (ChiVO)}
    {DevOps}
    {Valparaíso, Chile}
    {Jan. 2018 - May. 2018}
    {
      \begin{cvitems}
        \item {The FONDEF IT15I10041 project seeks to achieve the implementation of a virtual observatory in Chile that complies with the standards and protocols defined by the International Virtual Observatory Alliance (IVOA).}
        \item {We proposed and implemented a Cloud service where astronomers can safely use Jupyter notebooks over a personal space designed for high-performance processing using Docker Containers and Kubernetes.}
      \end{cvitems}
    }


  \cventry
    {Linets}
    {Systems Engineer}
    {Santiago, Chile}
    {Jan. 2014 - Mar. 2016}
    {
      \begin{cvitems}
        \item {System Administrator for upkeep, configuration, and reliable operation of 400 servers. The usual tasks were: troubleshooting, configuration, database administration, and optimization for the servers.}
        \item {Worked with OpenStack and main components to build the first OpenStack deployment in Chile which backs Beebop, the first public cloud in Chile.}
        \item {Automatic Deployment of OpenStack using Docker Containers and Ansible playbooks.}
        \item {Implementation of a shared storage for the public cloud using Ceph. Ceph is a unified, distributed storage system designed for excellent performance, reliability, and scalability.}
      \end{cvitems}
    }

  \cventry
    {Computer Science Department}
    {Systems Administrator}
    {Valparaíso, Chile}
    {Aug. 2011 - Oct. 2014}
    {
      \begin{cvitems}
		\item{System Administrator for the internal servers, maintaining all the services to ensure its availability to students and teachers.}
      \end{cvitems}
    }
\end{cventries}
