\cvsection{Skills}
\begin{cventries}
  \cvskill
  {Programming Languages}
  {Python, JavaScript, TypeScript, SQL, Bash}
  {Expert}
  {Proficient in developing applications, automating tasks, and analyzing data with these languages.}


  \cvskill
  {Web Frameworks}
  {React, FastAPI, Express, Django, LoopBack}
  {Expert}
  {Experienced in building dynamic and scalable web applications with modern frameworks and libraries.}


  \cventry
  {Cloud}
  {}
  {}
  {}
  {
    \begin{cvitems}
      \item {Excellent knowledge of OpenStack and its components; in
                  particular, Kolla. It provides Docker containers, Ansible
                  playbooks to deploy
                  OpenStack on bare-metal or virtual machines.}
      \item {Develop experience on Kubernetes and Docker.}
      \item {Familiar with virtualization technologies (KVM) and Cloud
                  providers (AWS, Digital Ocean, and Google Cloud).}
      \item {Good understanding of top-down TCP/IP stack.}
    \end{cvitems}
  }

  \cvskill
  {DevOps Tools}
  {Docker, Kubernetes, GitHub Actions, Ansible, Helm}
  {Proficient}
  {Experienced in containerization, orchestration, continuous integration, and deployment.}

  \cvskill
  {Cloud Platforms}
  {AWS, Azure}
  {Proficient}
  {Familiar with deploying and managing applications and services on major cloud platforms.}


  \cventry
  {Semantic Web}
  {RDF, OWL, SPARQL, Apache Jena, Neo4j}
  {Proficient}
  {
    \begin{cvitems}
      \item {Experience with RDF, Ontologies, SPARQL, Linked Data, and Apache
                  Jena. These tools were used to build DockerPedia.}
    \end{cvitems}
  }

\end{cventries}